\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{verbatim}
\textheight=10in
\pagestyle{empty}
\raggedbottom
\raggedright

% DEFINITIONS FOR RESUME

% Definition for the style of bullet to use
\newcommand{\mydot}{$\cdot$ }
%\newcommand{\mydot}{$\bullet$ }

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}

\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}

\newcommand{\contact}[3]{\vspace*{-8pt}\begin{center}{\LARGE \scshape {#1}}\\#2 \\ #3\end{center}\vspace*{-8pt}}

\newcommand{\school}[3]{\textbf{#1}{#2} \mydot #3 \\}

\newenvironment{courses}{\begin{list}{\mydot}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}

\newcommand{\seniorproject}[2]{Senior Project: #1\\ #2  }

\newcommand{\employer}[3]{\textbf{#1} (#2)\\ \emph{#3}\\  }

\newcommand{\project}[3]{\textbf{#1} (#2) \emph{#3}\\  }

\newenvironment{achievements}{\begin{list}{\mydot}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

% HEADER

\contact{Brian M. Partridge}
{258 Ash St. Waltham, MA 02453}
{
(781) 801-8844
\mydot brianpartridge@gmail.com 
%\mydot multipleentendre.com
}

% EDUCATION

\header{Education}
\school{Worcester Polytechnic Institute}{, Worcester, MA}{Bachelor of Science in Computer Science, 2006}

\begin{comment}
Selected Coursework:
\vspace*{-10pt}
\begin{multicols}{3}
\begin{courses}
  \item Operating Systems
  \item Distributed Computer Systems
  \item Software Engineering
  \item Computer Networks
  \item Human-Computer Interaction
  \item Databases
  \item Algorithms
  \item Webware
\end{courses}
\end{multicols}
\vspace*{-12pt}
\end{comment}

%\begin{comment}
\seniorproject{BitTorrent Subscriptions}{
\begin{achievements}
  \item Designed an online content distribution platform utilizing the BitTorrent protocol and RSS feeds.
  \item Extended a web based console for content creators to manage distribution of content.
  \item Implemented a client application facilitating subscription to and retrieval of content.
\end{achievements}
}
%\end{comment}

% WORK

\header{Work History}
\employer{EMC Corporation}{June 2006 - present}{Senior Software Engineer}
\begin{achievements}
  \item Served as a member of teams focused on developing various management and backup applications for EMC's flagship product, the \textbf{Symmetrix}.
  \item Responsible for developing storage provisioning functionality for the EMC Virtual Storage Integrator (VSI) plug-in for the VMware vSphere client.  Utilized reverse engineering technologies to enable the display of contextual information and perform storage operations directly on VMware entities in the vSphere GUI. (\textbf{C\#})
  \item Designed an interface for Virtual Machine Failback in VSI for use in disaster recovery scenarios to supplement VMware's Site Recovery Manager.
  \item Designed a library to integrate EMC software with VMware Virtual Infrastructure environments using the VMware SOAP web services.  The library is utilized by essential Symmetrix management utilities, including \textbf{Solutions Enabler} and backup products for Microsoft Exchange and SQL Server. (\textbf{C++})
  \item Re-engineered a legacy storage management utility with enhanced functionality using Microsoft VDS.
  \item Maintained a product providing an interface to physical storage information with various file systems and logical volume managers.
  \item Experience with version control software in a very large code base.
  \item Experience working with a team and independently.
  \item Strong understanding of enterprise storage technologies.
\end{achievements}

\employer{Shannon Systems}{Summer 2004 and 2005}{Software Engineering Intern}
\begin{achievements}
  \item Developed scripts for EDI processing of purchase order data between companies.
\end{achievements}

% PROJECTS

\header{Personal Projects}
\project{LazyEye}{2011}{iPhone App}{
\begin{achievements}
  \item A reading app, utilizing Rapid Serial Visual Presentation (RSVP) for fast reading speeds.
  \item Capable of extracting text from a website for clear, distraction-free reading.
\end{achievements}}
\project{Six Degrees}{2009}{iPhone App}{
\begin{achievements}
  \item Utilizes the Six Degrees of Separation concept to display links between actors and films.
  \item Provides several modes of operation for reference and entertainment purposes.
\end{achievements}}

% SKILLS

\header{Skills Summary}
\textbf{Programming Languages:} 
\begin{achievements}
  \item Proficient with C\#, Objective-C, C++, C
  \item Competent with Python
\end{achievements}
\vspace{-3pt}

\textbf{Frameworks \& APIs:} VMware Web Services SDK, .NET, Windows Forms, Cocoa Touch\\

\textbf{Operating Systems:} Windows, Mac OSX, Linux\\

\textbf{Tools:} Visual Studio, Xcode, CVS, vim, git\\

\end{document}

